Learning Distributed Word Representations for Natural Logic Reasoning

### 2015-01-09 writing/AAAI SSS '15/BowmanPottsManning/BowmanPottsManning.tex
AAAI formatted SSS submission

We build embedding-based models using the method of
\cite{Bowman:Potts:Manning:2014}, which is centered on the task of
labeling a pair of words or sentences with one of a small set of
logical relations. Unlike in a classical inference
setting, the model is not given specific premises to reason with at test time, but rather
is expected to encode all of the information that it learns about each term (word) at training
time in the term vectors, and to then use only the information encoded in the relevant pair of
term vectors at test time. 
The architecture that we use, which is limited to
only pairs of single terms, is depicted in
Figure~\ref{sample-figure}. The model represents the two input terms
as embeddings, which are fed into a comparison function based on one
of two types of neural network layer functions to produce a
representation for the relationship between the two terms. This
representation is then fed into a softmax classifier, which outputs a
distribution over possible labels. The entire network, including the
embeddings, is trained using backpropagation with AdaGrad \cite{duchi2011adaptive}
with L2 regularization.

@@

	  \textlabel{6.5,0.5}{Learned word vectors}{black}

@@

	\end{picture}
	%}
        \caption{The model structure used to compare \ii{turtle} and
          \ii{animal}.  Learned word representations are fed through
          either an NN or NTN comparison layer and then to a softmax
        classifier over the seven relations in Table~\ref{b-table}.}
  \label{sample-figure}
\end{figure}

@@

\paragraph{Experiments}
To test our models' ability to learn these inferential patterns, we
create artificial boolean structures in which terms denote sets of entities from
a small domain (e.g., Figure~\ref{lattice-figure}), employ logical
deduction to identify the valid statements, divide those into train
and test sets, and remove from the test set those statements which
cannot be proven from the training statements
(Figure~\ref{unprovable}). 
% using the logic depicted in Figure~\ref{lattice-figure}.
%
%
% We test the model's ability to learn this behavior by creating
% artificial data sets of terms which represent sets of numbers. Since
% MacCartney and Manning's set of relations hold between sets as well as
% between sentences, we can use the underlying set structure to generate
% the all of the relations that hold between any pair of these terms, as
% in Figure \ref{lattice-figure}. We train the model defined above on a
% subset of these relations, but rather then presenting the model with a
% pair of tree-structured sentences as inputs, simply present it with
% two single terms, each of which corresponds to a single vector in the
% (randomly initialized) vocabulary matrix $V$, ensuring that the model
% has no information about the terms being compared except the relations
% between them.
%
In our experiments, we create 80 randomly generated sets drawn from a
domain of seven elements. This yields 6400 statements about pairs of
formulae, of which 3200 are chosen as a test set. For 240 of the test examples, 
there is not sufficient evidence in the training data to support the choice of any 
one relation, and we  exclude these from our primary test set. 
We trained both the NN model and the 
NTN model on these data sets.

@@

\bibliography{MLSemantics} 
\bibliographystyle{aaai}

>>>>

We build embedding-based models using the method of
\cite{Bowman:Potts:Manning:2014}, which is centered on the task of
labeling a pair of words or sentences with one of a small set of
logical relations. Unlike in a classical inference
setting, the model is not given specific premises to reason with at test time, but rather
is expected to encode all of the information that it learns about each term (word) at training
time in the term embedding vectors, and to then use only the information encoded in the relevant pair of
term vectors at test time. 
The architecture that we use is depicted in
Figure~\ref{sample-figure}. The model represents the two input terms
as single embedding vectors, which are fed into a comparison function based on one
of two types of neural network layer function to produce a
representation for the relationship between the two terms. This
representation is then fed into a softmax classifier, which outputs a
distribution over possible labels. The entire network, including the
embeddings, is trained using backpropagation with AdaGrad \cite{duchi2011adaptive}
and L2 regularization.

@@

	  \textlabel{6.5,0.5}{Learned term vectors}{black}

@@

	\end{picture}
	%}
        \caption{The model structure used to compare \ii{turtle} and
          \ii{animal}.  Learned term representations are fed through
          either an NN or NTN comparison layer and then to a softmax
        classifier over the seven relations in Table~\ref{b-table}.}
  \label{sample-figure}
\end{figure}

@@

\paragraph{Experiments}
To test our models' ability to learn these inferential patterns, we
create artificial boolean structures in which terms denote sets of entities from
a small domain (e.g., Figure~\ref{lattice-figure}), employ logical
deduction to identify the valid statements, divide those into train
and test sets, and remove from the test set those statements which
cannot be proven from the training statements
(Figure~\ref{unprovable}). 
% using the logic depicted in Figure~\ref{lattice-figure}.
%
%
% We test the model's ability to learn this behavior by creating
% artificial data sets of terms which represent sets of numbers. Since
% MacCartney and Manning's set of relations hold between sets as well as
% between sentences, we can use the underlying set structure to generate
% the all of the relations that hold between any pair of these terms, as
% in Figure \ref{lattice-figure}. We train the model defined above on a
% subset of these relations, but rather then presenting the model with a
% pair of tree-structured sentences as inputs, simply present it with
% two single terms, each of which corresponds to a single vector in the
% (randomly initialized) vocabulary matrix $V$, ensuring that the model
% has no information about the terms being compared except the relations
% between them.
%
In our experiments, we create 80 randomly generated sets drawn from a
domain of seven elements. This yields 6400 statements about pairs of
formulae, of which 3200 are chosen as a test set. 240 of the test examples 
were excluded from the primary test set for lack of evidence in the training 
data to support the choice of any one relation. 
We then trained and evaluated both the NN model and the NTN model on these data sets.

@@

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Baroni \bgroup et al\mbox.\egroup
  }{2012}]{baroni2012entailment}
Baroni, M.; Bernardi, R.; Do, N.-Q.; and Shan, C.-c.
\newblock 2012.
\newblock Entailment above the word level in distributional semantics.
\newblock In {\em Proc. EACL}.

\bibitem[\protect\citeauthoryear{Bowman, Potts, and
  Manning}{2014}]{Bowman:Potts:Manning:2014}
Bowman, S.; Potts, C.; and Manning, C.
\newblock 2014.
\newblock Recursive neural networks can learn logical semantics.
\newblock {arXiv} manuscript 1406.1827.

\bibitem[\protect\citeauthoryear{Chen \bgroup et al\mbox.\egroup
  }{2013}]{chen2013learning}
Chen, D.; Socher, R.; Manning, C.; and Ng, A.
\newblock 2013.
\newblock Learning new facts from knowledge bases with neural tensor networks
  and semantic word vectors.
\newblock In {\em Proc. {ICLR}}.

\bibitem[\protect\citeauthoryear{Clark, Coecke, and
  Sadrzadeh}{2011}]{ClarkCoeckeSadrzadeh2011}
Clark, S.; Coecke, B.; and Sadrzadeh, M.
\newblock 2011.
\newblock Mathematical foundations for a compositional distributed model of
  meaning.
\newblock {\em Linguistic Analysis} 36(1--4):345--384.

\bibitem[\protect\citeauthoryear{Collobert \bgroup et al\mbox.\egroup
  }{2011}]{collobert2011natural}
Collobert, R.; Weston, J.; Bottou, L.; Karlen, M.; Kavukcuoglu, K.; and Kuksa,
  P.
\newblock 2011.
\newblock Natural language processing (almost) from scratch.
\newblock {\em JLMR} 12.

\bibitem[\protect\citeauthoryear{Duchi, Hazan, and
  Singer}{2011}]{duchi2011adaptive}
Duchi, J.; Hazan, E.; and Singer, Y.
\newblock 2011.
\newblock Adaptive subgradient methods for online learning and stochastic
  optimization.
\newblock {\em JMLR}.

\bibitem[\protect\citeauthoryear{Fellbaum}{2010}]{fellbaum2010wordnet}
Fellbaum, C.
\newblock 2010.
\newblock Word{N}et.
\newblock In {\em Theory and Applications of Ontology: Computer Applications}.
  Springer.

\bibitem[\protect\citeauthoryear{Grefenstette}{2013}]{grefenstette2013towards}
Grefenstette, E.
\newblock 2013.
\newblock Towards a formal distributional semantics: Simulating logical calculi
  with tensors.
\newblock arXiv manuscript 1304.5823.

\bibitem[\protect\citeauthoryear{Hermann, Grefenstette, and
  Blunsom}{2013}]{Hermann-etal:2013}
Hermann, K.; Grefenstette, E.; and Blunsom, P.
\newblock 2013.
\newblock ``{N}ot not bad'' is not ``bad'': A distributional account of
  negation.
\newblock In {\em Proc. of the 2013 Workshop on Continuous Vector Space Models
  and their Compositionality}.

\bibitem[\protect\citeauthoryear{Hitzler, H{{\"o}}lldobler, and
  Seda}{2004}]{hitzler2004logic}
Hitzler, P.; H{{\"o}}lldobler, S.; and Seda, A.~K.
\newblock 2004.
\newblock Logic programs and connectionist networks.
\newblock {\em Journal of Applied Logic} 2(3).

\bibitem[\protect\citeauthoryear{H{\"o}lldobler, Kalinke, and
  St{\"o}rr}{1999}]{holldobler1999approximating}
H{\"o}lldobler, S.; Kalinke, Y.; and St{\"o}rr, H.-P.
\newblock 1999.
\newblock Approximating the semantics of logic programs by recurrent neural
  networks.
\newblock {\em Applied Intelligence} 11(1).

\bibitem[\protect\citeauthoryear{Icard and Moss}{2013a}]{Icard:Moss:2013}
Icard, T., and Moss, L.
\newblock 2013a.
\newblock A complete calculus of monotone and antitone higher-order functions.
\newblock In {\em Proc. Topology, Algebra, and Categories in Logic}.

\bibitem[\protect\citeauthoryear{Icard and Moss}{2013b}]{Icard:Moss:2013:LILT}
Icard, T., and Moss, L.
\newblock 2013b.
\newblock Recent progress on monotonicity.
\newblock {\em Linguistic Issues in Language Technology} 9(7).

\bibitem[\protect\citeauthoryear{Katz}{1972}]{Katz72}
Katz, J.~J.
\newblock 1972.
\newblock {\em Semantic Theory}.
\newblock New York: Harper \& Row.

\bibitem[\protect\citeauthoryear{Maas, Hannun, and Ng}{2013}]{maasrectifier}
Maas, A.; Hannun, A.; and Ng, A.
\newblock 2013.
\newblock Rectifier nonlinearities improve neural network acoustic models.
\newblock In {\em Proc. ICML}.

\bibitem[\protect\citeauthoryear{MacCartney and
  Manning}{2009}]{maccartney2009extended}
MacCartney, B., and Manning, C.
\newblock 2009.
\newblock An extended model of natural logic.
\newblock In {\em Proc. IWCS}.

\bibitem[\protect\citeauthoryear{Miller}{1995}]{WordNet95}
Miller, G.~A.
\newblock 1995.
\newblock Word{N}et: A lexical database for {E}nglish.
\newblock {\em Communications of the {ACM}} 38(11):39--41.

\bibitem[\protect\citeauthoryear{Pennington, Socher, and
  Manning}{2014}]{pennington2014glove}
Pennington, J.; Socher, R.; and Manning, C.
\newblock 2014.
\newblock Glo{V}e: {G}lobal vectors for word representation.
\newblock In {\em Proc. EMNLP}.

\bibitem[\protect\citeauthoryear{Rei and Briscoe}{2014}]{rei2014looking}
Rei, M., and Briscoe, T.
\newblock 2014.
\newblock Looking for hyponyms in vector space.
\newblock In {\em Proc. {CoNLL}}.

\bibitem[\protect\citeauthoryear{Rockt{\"a}schel \bgroup et al\mbox.\egroup
  }{2014}]{rocktaschellow}
Rockt{\"a}schel, T.; Bosnjak, M.; Singh, S.; and Riedel, S.
\newblock 2014.
\newblock Low-dimensional embeddings of logic.
\newblock In {\em Proc. the ACL 2014 Workshop on Semantic Parsing}.

\bibitem[\protect\citeauthoryear{Socher \bgroup et al\mbox.\egroup
  }{2011}]{socher2011semi}
Socher, R.; Pennington, J.; Huang, E.; Ng, A.; and Manning, C.
\newblock 2011.
\newblock Semi-supervised recursive autoencoders for predicting sentiment
  distributions.
\newblock In {\em Proc. EMNLP}.

\bibitem[\protect\citeauthoryear{Sutskever, Vinyals, and
  Le}{2014}]{sutskever2014sequence}
Sutskever, I.; Vinyals, O.; and Le, Q.
\newblock 2014.
\newblock Sequence to sequence learning with neural networks.
\newblock In {\em Proc. {NIPS}}.

\bibitem[\protect\citeauthoryear{van Benthem}{2008}]{vanBenthem08NATLOG}
van Benthem, J.
\newblock 2008.
\newblock A brief history of natural logic.
\newblock In Chakraborty, M.; L{\"o}we, B.; Nath~Mitra, M.; and Sarukki, S.,
  eds., {\em Logic, Navya-Nyaya and Applications: Homage to {B}imal {M}atilal}.

\end{thebibliography}
\bibliographystyle{aaai}
